\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}

\title{CSC111 Winter 2026 Project 1}
\author{Sanghyun (Logan) Choo, Mupin (Jay) An}
\date{\today}

\begin{document}
\maketitle

\section*{Running the game}
The game can be run by executing \texttt{adventure.py}.
All game logic, including movement, inventory, scoring, and locked-location
checking, is handled within this file.

\section*{Game Map}

\begin{verbatim}
1   2  -1   4
5  -1  -1   8
9  10  11  12
13  14  15  16
\end{verbatim}

\textbf{Location details:}
\begin{itemize}
    \item Location 1: Front Campus (Starting location)
    \item Location 2: University College
    \item Location 4: Second Cup (T-card, Lucky Mug)
    \item Location 5: McLennan Labs
    \item Location 8: Woodsworth College
    \item Location 9: Trinity College
    \item Location 10: New College
    \item Location 11: Bahen Centre (USB Drive, Laptop Charger)
    \item Location 12: Earth Sciences Centre
    \item Location 13: Robarts Library (Dorm Key) – \textbf{LOCKED: Requires T-card}
    \item Location 14: Sidney Smith Hall
    \item Location 15: Oak House – \textbf{LOCKED: Requires Dorm Key, Deposit location}
    \item Location 16: Athletic Centre
\end{itemize}

Starting location: Location 1 (Front Campus)

\section*{Game Solution}

The optimal solution requires 30 total commands and 19 movement commands.

\textbf{Strategy:}
\begin{itemize}
    \item Pick up the T-card at Second Cup (Location 4).
    \item Use the T-card to unlock Robarts Library (Location 13).
    \item Pick up the Dorm Key inside Robarts.
    \item Use the Dorm Key to unlock Oak House (Location 15).
    \item Deposit all three required items (Lucky Mug, USB Drive, Laptop Charger) at Oak House.
\end{itemize}

\textbf{Command list:}

\begin{verbatim}
go south
go south
go east
go east
go east
go north
go north
pick up lucky mug
pick up t-card
go south
go south
go west
go west
go south
drop lucky mug
go west
pick up dorm key
go east
drop t-card
pick up lucky mug
go east
deposit lucky mug
go north
pick up laptop charger
go south
deposit laptop charger
go north
pick up usb drive
go south
deposit usb drive
\end{verbatim}

\textbf{Total movement commands:} 19

\textbf{Maximum score:} 185 points

\section*{Lose Condition}

The player loses the game if they exceed the maximum allowed number of
movement commands (50).

\textbf{Example command sequence leading to loss:}

\begin{verbatim}
go south
go north
(repeated until exceeding 50 movement commands)
\end{verbatim}

\textbf{Code locations:}
\begin{itemize}
    \item \texttt{adventure.py}: movement counter logic
    \item \texttt{adventure.py}: game-over check when moves exceed limit
\end{itemize}

\section*{Inventory}

\textbf{Locations involving items:}
\begin{itemize}
    \item Location 4: T-card, Lucky Mug
    \item Location 11: USB Drive, Laptop Charger
    \item Location 13: Dorm Key
    \item Location 15: Deposit location
\end{itemize}

\textbf{Example inventory demonstration:}

\begin{verbatim}
go south
go south
go east
go east
go east
go north
go north
pick up lucky mug
inventory
\end{verbatim}

This demonstrates picking up an item and checking the inventory.

\textbf{Inventory handling code:}
\begin{itemize}
    \item \texttt{AdventureGame.__init__()} initializes \texttt{inventory}
    \item \texttt{"inventory"} command handler in \texttt{adventure.py}
    \item Pick-up logic checks inventory capacity (maximum of 2 items)
\end{itemize}

\section*{Score}

Players earn points by depositing required items at Oak House (Location 15).

\begin{itemize}
    \item USB Drive: 50 points
    \item Laptop Charger: 75 points
    \item Lucky Mug: 60 points
\end{itemize}

\textbf{First possible score increase:} Depositing Lucky Mug at Location 15.

\textbf{Score-related code:}
\begin{itemize}
    \item \texttt{AdventureGame.score} attribute
    \item \texttt{"score"} command handler
    \item Deposit logic adds \texttt{item.target\_points} to total score
    \item \texttt{Item} class stores \texttt{target\_points}
\end{itemize}

\section*{Enhancements}

\subsection*{1. Separate Drop and Deposit Commands (Medium Complexity)}

Players can either:
\begin{itemize}
    \item \texttt{drop} an item (leave it at current location), or
    \item \texttt{deposit} an item (score points at Oak House).
\end{itemize}

This required separate logic for:
\begin{itemize}
    \item Updating inventory
    \item Updating location item lists
    \item Checking valid deposit location
\end{itemize}

\subsection*{2. Locked Locations with Key Items (Medium Complexity)}

Two locations are locked:
\begin{itemize}
    \item Robarts Library requires the T-card
    \item Oak House requires the Dorm Key
\end{itemize}

Before allowing entry, the game checks whether the required key item is
present in the player's inventory.

Additionally, the game prevents the player from dropping a key item in a
location where they would be permanently locked out.

\subsection*{3. Movement-Based Lose Condition (Medium Complexity)}

The game tracks movement commands separately from other commands.

If the player reaches 50 movement commands (i.e., 50 ``go'' commands),
the game ends in a loss. Non-movement commands such as
``pick up'', ``drop'', ``deposit'', ``inventory'', and ``score''
do not increase the move count.

This required:
\begin{itemize}
    \item Tracking movement commands only
    \item Incrementing the counter only for ``go'' commands
    \item Checking the limit after each movement
\end{itemize}

\end{document}
